Quantifying Uncertainty in Forecast-Based Anticipatory Action Triggers Using Bootstrapping Methods

### 2025-09-20 paper.tex
latest text update, w/ nathan's edits

To test how sensitive the protocol is to the exact threshold values chosen, this section presents an uncertainty analysis. This analysis is based on the method of re-estimating the trigger threshold with resampled draws of the historical record, known as bootstrappaing [cite]. Repeating this procedure many times gives us an estimated distribution of how much the threshold might be expected to vary due to sampling error of a limited historical record. In this case, we run 1,000 iterations of the re-sampling process. In each iteration, we draw a sample of equal size to the original data comprised of randomly sampled blocks of 5 consecutive years, sampled with replacement. The block width of 5 was chosen here to account for the timescale of common sources of interannual correlation like ENSO.

@@

>>>>

To test how sensitive the protocol is to the exact threshold values chosen, this section presents an uncertainty analysis. This analysis is based on the method of re-estimating the trigger threshold with resampled draws of the historical record, known as bootstrapping [cite]. Repeating this procedure many times gives us an estimated distribution of how much the threshold might be expected to vary due to sampling error of a limited historical record. In this case, we run 1,000 iterations of the re-sampling process. In each iteration, we draw a sample of equal size to the original data comprised of randomly sampled blocks of 5 consecutive years, sampled with replacement. The block width of 5 was chosen here to account for the timescale of common sources of interannual correlation like ENSO.

@@

% take a look at Kevin's github for some references of how to code this

% discuss how uncertainty increases as frequency increases
